---
title: "Week 6 Lab"
author: "Michelle Lepori-Bui"
date: "11/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```

## Intro to Linear Regression

First create two sample vectors.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)

```

Is there evidence for a significant difference in ranks between the populations from which gp_1 and gp_2 where drawn?

Visualize data with base r 

```{r}
hist(gp_1)
hist(gp_2)
```

Not normally distributed
small sample size
Medians are better metric 

Mann-Whitney U

```{r}
my_mwu <- wilcox.test(gp_1, gp_2)
```

### Simple linear regression

A. Look at it!

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point()
```


```{r}
# Linear model, stored as penguin_lm:
penguin_lm <- lm(body_mass_g ~flipper_length_mm, data = penguins)

# Return the complete overview:
summary(penguin_lm)
```



Use broom::tidy() to access model outputs more easily

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

# get the intercept:
penguin_int <- penguin_lm_tidy$estimate[1]
penguin_int
```

```{r}
# flipper_length coefficient:
penguin_coef <- penguin_lm_tidy$estimate[2]
penguin_coef
```

```{r}
# metrics at a glance:

penguin_lm_out <- broom::glance(penguin_lm)
penguin_lm_out


```























